Hydras \& Co.

### 2022-05-23 doc/hydras.tex
update bibliography

This document is \emph{not} an introductory text for \coq, and there are many aspects of this proof assistant that are not covered. 
 The reader should already have some basic experience with the \coq system. The Reference Manual and several tutorials are available on the \coq website~\cite{Coq}. The first chapters of textbooks like \emph{Interactive Theorem Proving and Program Development}~\cite{BC04}, \emph{Software Foundations}~\cite{SF} or  \emph{Certified Programming with Dependent Types} ~\cite{chlipalacpdt2011} will give you the right background.

>>>>

This document is \emph{not} an introductory text for \coq, and there are many aspects of this proof assistant that are not covered. 
The reader should already have some basic experience with the \coq system. The Reference Manual and several tutorials are available on the \coq website~\cite{Coq}. The first chapters of textbooks like \emph{Interactive Theorem Proving and Program Development}~\cite{BC04},
\emph{Software Foundations}~\cite{SF},
\emph{Programs and Proofs}~\cite{Sergey:PnP},
or  \emph{Certified Programming with Dependent Types} ~\cite{chlipalacpdt2011} will give you the right background.
